Recruitment rate estimation in waterfowl using a non-invasive method

### 2021-12-14 Code/Draft_ruddy_duck_recruitment_rate.Rmd
update before conflict text

The recruitment rates from the counting method are in the same range for the two populations. The higher variability observed in France is not unexpected because the French time series is longer than in UK and corresponds to a larger harvest spectrum. There is no temporal correlation between the two populations, so it suggests that the recruitment rate is more likely influenced by regional-scale factors than large-scale ones. This is consistent with the literature because **[ref required]** shows that nesting success and hatching success are conditional to water levels, and that juvenile survival in waterfowl depends mostly on weather conditions [@Blums2004].

Assuming that the sample data provide a good picture of the interannual variability of the recruitment rate, the good correlation to the outputs of the counting method demonstrates its ability to track the recruitment rate variability. This result is quite robust because the correlation is obvious with only five years available. However, this conclusion might be overrated because two successive population size values are part of the recruitment rate, which mechanically scale the outputs. It explains why the correlation on the immature proportion, the other component of the recruitment rate, is a bit less obvious than for the recruitment rate (Figure \@ref(fig:sup)A).

@@

>>>>

The recruitment rates from the counting method are in the same range for the two populations. The higher variability observed in France is not unexpected because the French time series is longer and covers a larger harvest spectrum than in UK. There is no temporal correlation between the two populations, so it suggests that the recruitment rate is more likely influenced by regional-scale factors than large-scale ones. This is consistent with the literature because both nesting/hatching success and juvenile survival are conditional to the onset of lay, which is tightly related to local weather parameters, i.e. the spring temperature, the cumulative rainfall, and the water levels [@Folliot2017; @Blums2004; @Dzus1998].

Assuming that the sample data provide a good picture of the interannual variability of the recruitment rate, the good correlation to the outputs of the counting method demonstrates its ability to track the recruitment rate variability. This result is quite robust because the correlation is obvious with only a five-year time series. However, this conclusion might be overrated because two successive population size values are part of the recruitment rate, which mechanically scale the outputs. It explains why the correlation on the immature proportion, the other component of the recruitment rate, is a bit more noisy than for the recruitment rate (Figure \@ref(fig:sup)A).

@@

Variability within harvest category represents
